---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# ggls

<!-- badges: start -->
[![R-CMD-check](https://github.com/beabock/ggls/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/beabock/ggls/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

The goal of ggls is to add letter indicating the significance of differences of results among treatments displayed in ggplot barplots and boxplots.

## Installation

You can install the development version of ggls from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("beabock/ggls")
```

## Example

If you want to use the ggpubr package, you may need to create a list of comparisons for the groups you want to compare. If you want to compare all groups to each other, this command does that.

```{r example, warning = FALSE, error= FALSE, message= FALSE}
library(ggls)

comparison_maker(ToothGrowth, supp)
```

Additionally, if you are using ggpubr, you may want to test the common assumptions of common statistical tests on your dataset. The test_assumptions function does this.

```{r example2}

test_assumptions(ToothGrowth, supp, len)

```






You'll still need to render `README.Rmd` regularly, to keep `README.md` up-to-date. `devtools::build_readme()` is handy for this.



